\tlatex
\setboolean{shading}{true}
\@x{}\moduleLeftDash\@xx{ {\MODULE} CancellationMch1}\moduleRightDash\@xx{}%
\@x{ {\EXTENDS} CancellationCtx1 ,\, Policy ,\, Sequences}%
\@pvspace{8.0pt}%
 \@x{ {\CONSTANTS} policyTi ,\, policyTf ,\, reinstatementExpireDays ,\,
 Documents}%
\@pvspace{8.0pt}%
\@x{ {\VARIABLES} policy ,\, step ,\, mods ,\, term}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Here, I model the state by separating it into a \ensuremath{Policy} state and
 a Modification Set
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 state. Within the Modification Set, each Modification follows a stand alone,
 independent
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 state machine which in greatest generality is . \ensuremath{\.{\rightarrow}
 Created \.{\rightarrow}} Accepted \ensuremath{\.{\rightarrow}
 Issued \.{\,|\,}} Invalidated \ensuremath{\.{\rightarrow}} . A
 \ensuremath{Policy} only listens to \ensuremath{Issued} events, and rolls
 forward its
 state on those events.
 In the system all modifications are retained but for this
 abstractions only issued modifications are recorded. This omission reduces
 the state
 space, but it also suggests an important insight, that modifications in the
 \ensuremath{Created
} state have little processing significance.
\end{cpar}%
\end{lcom}%
\@x{}\midbar\@xx{}%
\@x{}%
\@y{\@s{0}%
 Functions
}%
\@xx{}%
\@x{ prevMod \.{\defeq} \.{\LET} last \.{\defeq} Len ( mods )}%
 \@x{\@s{56.61} \.{\IN} {\IF} last \.{=} 0 \.{\THEN} NoModification \.{\ELSE}
 mods [ last ]}%
\@pvspace{8.0pt}%
\@x{ pendingReinstatementExpired ( p ) \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} p . pending\_modification}%
 \@x{\@s{16.4} \.{\IN} pending \.{\in} Reinstatements \.{\land} pending .
 deadline\_ts \.{<} step}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 Just a semantic addition to signify when we must invalidate a accepted
 modifications
}%
\@xx{}%
\@x{ invalidate ( mod ) \.{\defeq} {\TRUE}}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\@x{}%
\@y{\@s{0}%
 Invariants
}%
\@xx{}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
Cancellations and reinstatements, like endorsements and renewals, are recorded
 as they are created in a history of policy modifications. Some of those
 modifications
 will take effect, by being issued, others will never be issued. In all
 cases, though,
 modifications retain an identity to which documents and invoices can be
 attached. The
 characteristic of the above modifications, which gives them a group
 commonality, is
 that they can operate to change liability of the parties to the contract
\end{cpar}%
\end{lcom}%
\@x{ InvType \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
 \@x{\@s{16.4} \.{\IN} \.{\land} pending \.{\in} {\UNION} \{ Reinstatements
 ,\,}%
\@x{\@s{131.90} Cancellations ,\,}%
\@x{\@s{131.90} \{ NoModification ,\, EndorsementOrRenewal \}}%
\@x{\@s{131.90} \}}%
\@x{\@s{36.79} \.{\land} policy . state \.{\in} PolicyState}%
\@pvspace{8.0pt}%
\@x{ InvPolicy \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} policy . original\_start\_ts \.{=} policyTi}%
 \@x{\@s{36.79} \.{\land} pending \.{\notin} \{ NoModification ,\,
 EndorsementOrRenewal \} \.{\implies}}%
\@x{\@s{181.66} pending . state \.{=}\@w{Finalized}}%
\@x{\@s{36.79} \.{\land} policy . state \.{=}\@w{Cancelled} \.{\implies} (}%
\@x{\@s{56.11} pending \.{\neq} EndorsementOrRenewal}%
 \@x{\@s{56.11} \.{\land} policy . original\_start\_ts \.{=} policy .
 effective\_end\_ts )}%
\@x{\@s{36.79} \.{\land} (\@s{4.31} \.{\land} pending \.{\in} Reinstatements}%
 \@x{\@s{52.01} \.{\land} pending . auto\_reinstate ) \.{\implies} pending .
 deadline\_ts \.{+} 1 \.{\geq} step}%
\@pvspace{8.0pt}%
\@x{ InvMods \.{\defeq}}%
 \@x{\@s{16.4} \.{\LET}\@s{0.86} pending \.{\defeq} policy .
 pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} prevMod \.{\neq} NoModification \.{\implies}}%
 \@x{\@s{56.11} prevMod . start\_timestamp \.{\geq} policy .
 original\_start\_ts}%
 \@x{\@s{36.79} \.{\land} policy . state \.{=}\@w{Cancelled} \.{\implies}
 prevMod \.{\in} Cancellations}%
 \@x{\@s{36.79} \.{\land} policy . state \.{=}\@w{Cancelled} \.{\implies}
 pending\@s{3.62} \.{\in} Reinstatements \.{\cup} \{ NoModification \}}%
 \@x{\@s{36.79} \.{\land} \A\, idx \.{\in} 1 \.{\dotdot} Len ( mods ) \.{:}
 mods [ idx ] \.{\in} Cancellations \.{\implies}}%
 \@x{\@s{67.43} ( mods [ idx ] . start\_timestamp \.{<} mods [ idx ] .
 end\_timestamp )}%
 \@x{\@s{36.79} \.{\land} \A\, idx \.{\in} 2 \.{\dotdot} Len ( mods ) \.{:}
 mods [ idx ] \.{\in} Reinstatements \.{\implies}}%
 \@x{\@s{67.43} ( \.{\land} mods [ idx\@s{0.21} \.{-} 1 ] \.{\in}
 Cancellations}%
 \@x{\@s{71.53} \.{\land} mods [ idx \.{-} 1 ] . end\_timestamp \.{=} mods [
 idx ] . end\_timestamp )}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 As long as a policy is \ensuremath{OnRisk}, not fully canceled, endorsements
 or renewals for the
 policy may transition into an accepted state, creating a pending modification
\end{cpar}%
\end{lcom}%
\@x{ acceptGeneric \.{\defeq}}%
\@x{\@s{16.4} \.{\land} step \.{<} policyMaxTs}%
 \@x{\@s{16.4} \.{\land} policy . state \.{=}\@w{OnRisk} \.{\land} policy .
 pending\_modification \.{=} NoModification}%
 \@x{\@s{16.4} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} .
 pending\_modification \.{=} EndorsementOrRenewal ]}%
\@x{\@s{16.4} \.{\land} step \.{'} \.{=} step \.{+} 1}%
\@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} mods ,\, term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 A cancellation can be created on any policy that is \ensuremath{OnRisk}. The
 start date specified by
 the cancellation should be within the coverage time span of the policy.
 Note that for the specification, we do not have cancellation create events
 result in
 additions to the modifications set. This addition would ordinarily happen in
 a concrete
 implementation, however, we elide the effect here as maintaining basic
 policy state along
 with a list of just issued modifications is sufficient to validate
 consistency. The fact
 that this approach is sufficient, is an important insight into the minor
 significance of
 states other than Accepted and \ensuremath{Issued}.
\end{cpar}%
\end{lcom}%
\@x{ createCancellation ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{16.4} \.{\land} policy . state \.{=}\@w{OnRisk}}%
 \@x{\@s{16.4} \.{\land} mod . type \.{=}\@w{Cancellation} \.{\land} mod .
 state \.{=}\@w{Created}}%
 \@x{\@s{16.4} \.{\land} mod . start\_timestamp \.{<} policy .
 effective\_end\_ts}%
 \@x{\@s{16.4} \.{\land} mod . start\_timestamp \.{\geq} policy .
 original\_start\_ts}%
 \@x{\@s{16.4} \.{\land} {\lnot} pendingReinstatementExpired ( policy
 )\@s{16.4}}%
\@y{\@s{0}%
 assumed
}%
\@xx{}%
\@x{\@s{16.4} \.{\land} step \.{'} \.{=} step \.{+} 1}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} policy ,\, mods ,\, term
 {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 A cancellation can be issued whenever its policy is \ensuremath{OnRisk}.
 Further a cancellation can be
 issued regardless of any current, pending modifications on its policy. The
 only
 restriction is that the cancellation date must be within the time span of
 the policy. If
 any endorsement or renewals are pending then those must be invalidated.
\end{cpar}%
\end{lcom}%
\@x{ issueCancellation ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{36.79} \.{\land} policy . state \.{=}\@w{OnRisk}}%
 \@x{\@s{36.79} \.{\land} mod . type \.{=}\@w{Cancellation} \.{\land} mod .
 state \.{=}\@w{Created}}%
 \@x{\@s{36.79} \.{\land} mod . end\_timestamp \.{=} policy .
 effective\_end\_ts\@s{8.2}}%
\@y{\@s{0}%
 assumed
}%
\@xx{}%
 \@x{\@s{36.79} \.{\land} policy . original\_start\_ts \.{\leq} mod .
 start\_timestamp}%
 \@x{\@s{36.79} \.{\land} policy . effective\_end\_ts \.{>} mod .
 start\_timestamp}%
\@x{\@s{36.79}}%
\@y{\@s{0}%
 actions
}%
\@xx{}%
\@x{\@s{36.79} \.{\land} invalidate ( pending )}%
 \@x{\@s{36.79} \.{\land} {\CASE} policy . original\_start\_ts \.{=} mod .
 start\_timestamp \.{\rightarrow}}%
\@x{\@s{56.11} \.{\land}\@s{6.66} policy \.{'} \.{=} [ policy {\EXCEPT}}%
\@x{\@s{156.45} {\bang} . state \.{=}\@w{Cancelled} ,\,}%
\@x{\@s{156.45} {\bang} . pending\_modification \.{=} NoModification ,\,}%
\@x{\@s{156.45} {\bang} . effective\_end\_ts \.{=} mod . start\_timestamp ]}%
\@x{\@s{47.91} {\Box} {\OTHER} \.{\rightarrow}}%
\@x{\@s{56.11} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT}}%
\@x{\@s{149.78} {\bang} . pending\_modification \.{=} NoModification ,\,}%
\@x{\@s{149.78} {\bang} . effective\_end\_ts \.{=} mod . start\_timestamp ]}%
 \@x{\@s{36.79} \.{\land} mods \.{'} \.{=} Append ( mods ,\, [ mod {\EXCEPT}
 {\bang} . state \.{=}\@w{Issued} ] )}%
\@x{\@s{36.79} \.{\land} step \.{'}\@s{5.04} \.{=} step \.{+} 1}%
\@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 The legacy lapse action acts similarly to the above cancellation method. It
 can be
 thought of as the sequential application of a cancellation create + issue.
 There is a
 switch in the new cancellation configuration to disable the
 \ensuremath{legacyLapse} action, possibly
 but not preferably, as shown in the first guard condition below
\end{cpar}%
\end{lcom}%
\@x{ legacyLapse ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land}\@w{Lapse} \.{\notin} CancellationReasons}%
\@x{\@s{16.4} \.{\land} issueCancellation ( mod )}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 I have not included \ensuremath{legacyReinstatement} in the model, as one can
 see in the \ensuremath{Next} definition.
 Instead I just note that \ensuremath{legacyReinstatment} should equal the
 effect of consecutive draft,
 accept, issue operations in the new \ensuremath{API}, and so it is
 effectively already modeled.
 Because this function is defined as draft + accept + issue, the
 preconditions for this
 functions proper operation must be the conjunction of the guard conditions
 for draft,
 accept, and issue below.
\end{cpar}%
\end{lcom}%
\@x{ legacyReinstatement ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land}\@w{Lapse} \.{\notin} CancellationReasons}%
\@x{\@s{16.4} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{16.4} \.{\land} policy . state \.{=}\@w{Canceled}}%
 \@x{\@s{16.4} \.{\land} mod . type \.{=}\@w{Reinstatement} \.{\land} mod .
 state \.{=}\@w{Created}}%
 \@x{\@s{16.4} \.{\land} mod . start\_timestamp \.{<} policy .
 effective\_end\_ts}%
 \@x{\@s{16.4} \.{\land} mod . start\_timestamp \.{\geq} prevMod .
 start\_timestamp}%
\@x{\@s{16.4} \.{\land} mod . deadline\_ts \.{\geq} step}%
 \@x{\@s{16.4} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} . state
 \.{=}\@w{Issued} ,\,}%
\@x{\@s{139.79} {\bang} . pending\_modification \.{=} NoModification ]}%
 \@x{\@s{16.4} \.{\land} mods \.{'} \.{=} Append ( mods ,\, [ mod {\EXCEPT}
 {\bang} . state \.{=}\@w{Issued} ] )}%
\@x{\@s{16.4} \.{\land} step \.{'}\@s{5.04} \.{=} step \.{+} 1}%
\@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 If a policy is in the canceled state then we can begin a draft reinstatement
 to reinstate
 it. The draft must specify an effective start date within the timespan
 truncated by the
 cancellation which preceded it. For the purposes of specification, updating
 a draft
 reinstatement is modeled as having the same processing effect as adding a
 new draft to
 the modification set.
 As with \ensuremath{createCancellation} we don\mbox{'}t model the addition
 to the modification set, though
 that would be part of the concrete implementation. Also the specification
 here, again,
 points out the relative insignificance of modifications in the draft state.
\end{cpar}%
\end{lcom}%
\@x{ draftReinstatement ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
 \@x{\@s{36.79} \.{\land} mod . type \.{=}\@w{Reinstatement} \.{\land} mod .
 deadline\_ts \.{>} step}%
 \@x{\@s{36.79} \.{\land} mod . start\_timestamp \.{\geq} policy .
 effective\_end\_ts}%
\@x{\@s{36.79} \.{\land} mod . deadline\_ts \.{+} 1\@s{4.63} \.{<} step}%
\@x{\@s{36.79} \.{\land} prevMod \.{\in} Cancellations}%
 \@x{\@s{36.79} \.{\land} {\lnot} pendingReinstatementExpired ( policy
 )\@s{16.4}}%
\@y{\@s{0}%
 assumed
}%
\@xx{}%
\@x{\@s{36.79} \.{\land} step \.{'} \.{=} step \.{+} 1}%
 \@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} policy ,\, mods ,\, term
 {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 If a reinstatement exists past its \ensuremath{deadline\_ts} without being
 issued then it expires.
 At that point the reinstatement is removed as a pending modification, its
 documents are
 discarded, and its invoices are settled.
 Though not modeled here it is possible for a reinstatement in the draft
 state to expire.
 These can just be discarded.
\end{cpar}%
\end{lcom}%
\@x{ expireReinstatement \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{36.79} \.{\land} pendingReinstatementExpired ( policy )}%
\@x{\@s{36.79} \.{\land} invalidate ( pending )}%
 \@x{\@s{36.79} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} .
 pending\_modification \.{=} NoModification ]}%
\@x{\@s{36.79} \.{\land} step \.{'} \.{=} step \.{+} 1}%
\@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} mods ,\, term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 In order to accept a reinstatement the start date of the reinstatement must
 be within
 the time span truncated by the cancellation it follows. There must also be
 (1) no other
 accepted modifications pending and (2) (in this model) the most recently
 issued
 modification must be a \ensuremath{Cancellation}.
\end{cpar}%
\vshade{5.0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 (1) means the reinstatement waits, like other modification operations, when
 it is blocked.
 Formally it participates in the system Draft \ensuremath{\.{\rightarrow}}
 Accept \ensuremath{\.{\rightarrow}} Issue workflow. Note that
 this behavior is unlike the \ensuremath{Cancellation} workflow, which does
 not block and is
 privileged to clear the global accept lock when it does its work.
\end{cpar}%
\vshade{5.0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
(2) is a bit more restrictive than what we want for the concrete
 implementation where we will only insist that a cancellation designated in
 the request
 exists and has not since been followed by a renewal
\end{cpar}%
\end{lcom}%
\@x{ acceptReinstatement ( mod ) \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{36.79} \.{\land} pending \.{=} NoModification}%
 \@x{\@s{36.79} \.{\land} mod . type \.{=}\@w{Reinstatement} \.{\land} mod .
 state \.{=}\@w{Created} \.{\land} mod . deadline\_ts \.{>} step}%
 \@x{\@s{36.79} \.{\land} mod . start\_timestamp \.{\geq} policy .
 effective\_end\_ts}%
\@x{\@s{36.79} \.{\land} mod . start\_timestamp \.{<} mod . end\_timestamp}%
 \@x{\@s{36.79} \.{\land} prevMod \.{\in} Cancellations \.{\land} prevMod .
 end\_timestamp \.{=} mod . end\_timestamp}%
\@x{\@s{36.79} \.{\land} policy \.{'}\@s{9.24} \.{=} [ policy {\EXCEPT}}%
 \@x{\@s{127.42} {\bang} . pending\_modification \.{=} [ mod {\EXCEPT} {\bang}
 . state \.{=}\@w{Finalized} ] ]}%
\@x{\@s{36.79} \.{\land} step \.{'} \.{=} step \.{+} 1}%
\@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} mods ,\, term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Issuing a reinstatement reactivates the policy restoring the end date and
 coverage as
 of the previous cancellation.
 Note that with cancellations and reinstatements it becomes possible to have
 gaps in a
 policies coverage. These gaps will be of some potential concern for financial
 calculations and claim coverage. Gaps will also factor into the timestamps
 on peril
 characteristic records in ways that will need to be defined and documented.
\end{cpar}%
\end{lcom}%
\@x{ issueReinstatement \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{36.79} \.{\land} pending \.{\in} Reinstatements}%
 \@x{\@s{36.79} \.{\land} {\lnot} pendingReinstatementExpired ( policy
 )\@s{16.4}}%
\@y{\@s{0}%
 assumed
}%
\@xx{}%
 \@x{\@s{36.79} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} .
 state \.{=}\@w{OnRisk} ,\,}%
\@x{\@s{160.19} {\bang} . pending\_modification \.{=} NoModification ]}%
 \@x{\@s{36.79} \.{\land} mods \.{'} \.{=} Append ( mods ,\, [ pending
 {\EXCEPT} {\bang} . state \.{=}\@w{Issued} ] )}%
\@x{\@s{36.79} \.{\land} step \.{'}\@s{5.04} \.{=} step \.{+} 1}%
\@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 When we invalidate a reinstatement we return the modification to the draft
 state. We
 discard all documents associated with the reinstatement and then settle any
 invoices.
\end{cpar}%
\end{lcom}%
\@x{ invalidateReinstatement \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} pending \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
 \@x{\@s{36.79} \.{\land} pending \.{\in} Reinstatements \.{\land} step
 \.{\leq} pending . deadline\_ts}%
\@x{\@s{36.79} \.{\land} invalidate ( pending )}%
 \@x{\@s{36.79} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} .
 pending\_modification \.{=} NoModification ]}%
\@x{\@s{36.79} \.{\land} step \.{'} \.{=} step \.{+} 1}%
\@x{\@s{36.79} \.{\land} {\UNCHANGED} {\langle} mods ,\, term {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
If we receive a payment when we have a finalized reinstatement in the
 pending modifications set then the policy can be issued if
 \ensuremath{autoReinstate
} is on.
 The operation below is just a placeholder to make the existence of the auto
 reinstate
 functionality. Implementing it would just repeat the
 \ensuremath{issueReinstatement} operation
 above.
\end{cpar}%
\end{lcom}%
\@x{ payInvoiceReinstatement \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} mod \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
\@x{\@s{36.79} \.{\land} mod . auto\_reinstate \.{=} {\TRUE}}%
\@x{\@s{36.79} \.{\land} issueReinstatement}%
\@pvspace{8.0pt}%
\@x{ doStep \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} mod \.{\defeq} policy . pending\_modification}%
\@x{\@s{16.4} \.{\IN} \.{\land} step \.{<} policyMaxTs}%
 \@x{\@s{36.79} \.{\land} {\IF} ( \.{\land} mod \.{\notin} \{ NoModification
 ,\, EndorsementOrRenewal \}}%
\@x{\@s{64.16} \.{\land} mod . type \.{=}\@w{Reinstatement}}%
\@x{\@s{64.16} \.{\land} step \.{>} mod . deadline\_ts )}%
\@x{\@s{47.91} \.{\THEN} expireReinstatement}%
\@x{\@s{47.91} \.{\ELSE} \.{\land} step \.{'} \.{=} step \.{+} 1}%
 \@x{\@s{79.22} \.{\land} {\UNCHANGED} {\langle} policy ,\, term ,\, mods
 {\rangle}}%
\@pvspace{8.0pt}%
\@x{ doTerm \.{\defeq}}%
\@x{\@s{16.4} \.{\land}\@s{6.86} step \.{=} policyMaxTs}%
\@x{\@s{16.4} \.{\land}\@s{6.86} term \.{'} \.{=} {\TRUE}}%
 \@x{\@s{16.4} \.{\land}\@s{6.86} {\UNCHANGED} {\langle} policy ,\, step ,\,
 mods {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 General observations: For cancellations I believe that if we issue a policy
 from \ensuremath{t1} to
 \ensuremath{t3} and then cancel back to some intermediate time
 \ensuremath{t2}, the effect, from the pov of an
 external observer of total payments, should be as if the policy was issued
 from \ensuremath{t1} to \ensuremath{t2}.
 Or, more generally, there are many sequences where the following will hold
\end{cpar}%
\vshade{5.0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
Issue; Cancel; Reinstate; \ensuremath{\.{=}} Issue
\end{cpar}%
\vshade{5.0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 These sorts of relationship should be useful in checking the financial
 calculation
 routines to the extent they need to be checked.
\end{cpar}%
\end{lcom}%
\@x{}\midbar\@xx{}%
\@x{ Init \.{\defeq}}%
\@x{\@s{16.4} \.{\land} step \.{=} 0}%
\@x{\@s{16.4} \.{\land} policy \.{=} [}%
\@x{\@s{31.61} original\_start\_ts \.{\mapsto} policyTi ,\,}%
\@x{\@s{31.61} effective\_end\_ts \.{\mapsto} policyTf ,\,}%
\@x{\@s{31.61} billing\_policy \.{\mapsto}\@w{BySystemOnFinalize} ,\,}%
\@x{\@s{31.61} state \.{\mapsto}\@w{OnRisk} ,\,}%
 \@x{\@s{31.61} revision\_start\_timestamps \.{\mapsto} \{ {\langle} 0 ,\,
 policyTi {\rangle} \} ,\,}%
\@x{\@s{31.61} renewal\_start\_timestamps \.{\mapsto} \{ \} ,\,}%
\@x{\@s{31.61} pending\_modification \.{\mapsto} NoModification ]}%
\@x{\@s{16.4} \.{\land} mods \.{=} {\langle} {\rangle}}%
\@x{\@s{16.4} \.{\land} term\@s{1.71} \.{=} {\FALSE}}%
\@pvspace{8.0pt}%
\@x{ Next \.{\defeq}}%
\@x{\@s{16.4} \.{\lor} acceptGeneric}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Cancellations \.{:}
 createCancellation ( m )}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Cancellations \.{:}
 issueCancellation ( m )}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Cancellations \.{:} legacyLapse (
 m )}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Reinstatements \.{:}
 draftReinstatement ( m )}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Reinstatements \.{:}
 acceptReinstatement ( m )}%
\@x{\@s{16.4} \.{\lor} expireReinstatement}%
\@x{\@s{16.4} \.{\lor} issueReinstatement}%
\@x{\@s{16.4}}%
\@y{\@s{0}%
 \ensuremath{\.{\lor} \E\, m \.{\in} Reinstatements} :
 \ensuremath{legacyReinstatement(m)
}}%
\@xx{}%
\@x{\@s{16.4} \.{\lor} invalidateReinstatement}%
\@x{\@s{16.4} \.{\lor} doStep}%
\@x{\@s{16.4} \.{\lor} doTerm}%
 \@x{\@s{16.4} \.{\lor} ( term \.{=} {\TRUE} \.{\land} {\UNCHANGED} {\langle}
 policy ,\, step ,\, mods ,\, term {\rangle} )}%
\@pvspace{8.0pt}%
 \@x{ Spec \.{\defeq} Init \.{\land} {\Box} [ Next ]_{ {\langle} policy ,\,
 step ,\, mods ,\, term {\rangle}}}%
\@pvspace{8.0pt}%
\@x{}\bottombar\@xx{}%
\setboolean{shading}{false}
\begin{lcom}{0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
\ensuremath{\.{\,\backslash\,}}* Modification History
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Wed}
 \ensuremath{Jul} 08 19:38:24 \ensuremath{PDT} 2020 by \ensuremath{marco
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Thu}
 \ensuremath{Jul} 02 22:05:54 \ensuremath{PDT} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* \ensuremath{Created} Sat \ensuremath{Jun} 27
 21:12:50 \ensuremath{PDT} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\end{lcom}%
