\tlatex
\setboolean{shading}{true}
 \@x{}\moduleLeftDash\@xx{ {\MODULE}
 AutoGraceLapseInvoiceMch0}\moduleRightDash\@xx{}%
\@x{ {\EXTENDS} AutoGraceLapseInvoiceCtx0 ,\, FiniteSets ,\, TLC}%
\@x{ {\CONSTANTS} endTime}%
\@pvspace{8.0pt}%
\@x{ {\VARIABLES} invsIssued ,\, policy ,\, gracesUnsettled ,\, time}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\@x{}%
\@y{\@s{0}%
 The possible combinations of settlement status and invoice type
}%
\@xx{}%
\@x{ InvInvoices \.{\defeq}}%
\@x{\@s{16.4} \.{\land} \forall\, i \.{\in} invsIssued \.{:}}%
 \@x{\@s{48.01} \.{\land} i . settlementStatus \.{=}\@w{Outstanding}
 \.{\implies} i . settlementType \.{=}\@w{Null}}%
 \@x{\@s{48.01} \.{\land} i . settlementStatus \.{=}\@w{Settled} \.{\implies}
 i . settlementType \.{\in} \{}%
 \@x{\@s{78.28}\@w{ZeroDue} ,\,\@w{WrittenOff} ,\,\@w{Invalidated}
 ,\,\@w{Paid}}%
\@x{\@s{63.20} \}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 A policy is either on policy or off policy. If it is off policy then the
 policy is
 no longer being offered to the customer and there must be no outstanding
 invoices.
\end{cpar}%
\end{lcom}%
\@x{ InvPolicy \.{\defeq}}%
\@x{\@s{16.4} \.{\land} policy . startDt \.{\leq} policy . endDt}%
\@x{\@s{16.4} \.{\land} policy . startDt \.{=} policy . endDt \.{\implies}}%
 \@x{\@s{48.01} ( \{ i \.{\in} invsIssued \.{:} i . settlementStatus
 \.{=}\@w{Outstanding} \} \.{=} \{ \} )}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 There must be at most one unsetteled grace record per policy
}%
\@xx{}%
\@x{ InvGraceRecs \.{\defeq}}%
\@x{\@s{16.4} \.{\land} Cardinality ( gracesUnsettled ) \.{\leq} 1}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 If any outstanding policy invoices exist, then there must be a unsettled
 grace record
 for the policy. If there is an unsettled grace record then there must be an
 outstanding policy invoice.
\end{cpar}%
\end{lcom}%
\@x{ InvInvoicesGraceRecs \.{\defeq}}%
 \@x{\@s{16.4} \.{\land} \{ i \.{\in} invsIssued \.{:} \.{\land} i .
 settlementStatus \.{=}\@w{Outstanding}}%
 \@x{\@s{103.27} \.{\land} time \.{>} i . dueDt \} \.{\neq} \{ \} \.{\implies}
 gracesUnsettled \.{\neq} \{ \}}%
 \@x{\@s{16.4} \.{\land} gracesUnsettled \.{\neq} \{ \} \.{\implies} \exists\,
 i \.{\in} invsIssued \.{:}}%
\@x{\@s{150.17} \.{\land} i . settlementStatus \.{=}\@w{Outstanding}}%
\@x{\@s{150.17} \.{\land} i . dueDt \.{\leq} time}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 The scheduled grace job tries to find policies that (1) dont have any
 associated,
 unsettled grace records in the \ensuremath{grace\_period} table and (2) do
 have outstanding invoices
 that are past their due date. If it finds such records it adds them to the
 \ensuremath{grace\_period} table, which roughly can be thought of as a queue
 of jobs which may or may
 not get to the top of the queueu and cause a lapse (cancellation)
\end{cpar}%
\end{lcom}%
\@x{ autoGraceCanRun ( tm ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} gracesUnsettled \.{=} \{ \}}%
 \@x{\@s{16.4} \.{\land} \exists\, i \.{\in} invsIssued \.{:} i . dueDt \.{=}
 tm \.{\land} i . settlementStatus \.{=}\@w{Outstanding}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 The scheduled lapse job looks for unsettled records in the
 \ensuremath{grace\_period} period and
 cancels the associated policy if the end of the grace period
 \ensuremath{\.{<}} now.
\end{cpar}%
\end{lcom}%
 \@x{ autoLapseCanRun ( tm ) \.{\defeq} \exists\, g \.{\in} gracesUnsettled
 \.{:} g . endDt \.{=} tm}%
\@pvspace{8.0pt}%
\@x{ autoJobCanRun ( tm ) \.{\defeq}}%
\@x{\@s{16.4} \.{\lor} autoGraceCanRun ( tm )}%
\@x{\@s{16.4} \.{\lor} autoLapseCanRun ( tm )}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 the definition of containment for a point within a closed - open interval.
}%
\@xx{}%
 \@x{ contains ( interval ,\, t )\@s{5.78} \.{\defeq} interval . startDt
 \.{\leq} t \.{\land} t \.{<} interval . endDt}%
\@pvspace{8.0pt}%
\@x{ overdueInvoices ( invs ) \.{\defeq} \{ i \.{\in} invs \.{:}}%
\@x{\@s{32.8} \.{\land} i . settlementStatus \.{=}\@w{Outstanding}}%
\@x{\@s{32.8} \.{\land} i . dueDt \.{\leq} time \}}%
\@pvspace{8.0pt}%
 \@x{ max ( t1 ,\, t2 ) \.{\defeq} {\IF} t1 \.{>} t2 \.{\THEN} t1 \.{\ELSE}
 t2}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\@x{}%
\@y{\@s{0}%
 Extension is a generic operation extends a policy range, a renewal or
 reinstatement.
}%
\@xx{}%
\@x{ extend ( m ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} m . startDt \.{=} policy . endDt}%
\@x{\@s{16.4} \.{\land} m . startDt \.{<} m . endDt}%
 \@x{\@s{16.4} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} . endDt
 \.{=} m . endDt ]}%
\@x{\@s{16.4} \.{\land} invsIssued \.{'} \.{=} invsIssued \.{\cup} \{ [}%
\@x{\@s{48.01} totalDue \.{\mapsto} 10 ,\,}%
\@x{\@s{48.01} startDt \.{\mapsto} m . startDt ,\,}%
 \@x{\@s{48.01} dueDt \.{\mapsto} max ( m . startDt \.{+} 1 ,\, time \.{+} 1 )
 ,\,}%
\@x{\@s{48.01} settlementStatus \.{\mapsto}\@w{Outstanding} ,\,}%
\@x{\@s{48.01} settlementType \.{\mapsto}\@w{Null}}%
\@x{\@s{31.61} ] \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
\@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} gracesUnsettled {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
Reduce is a generic operation that reduces a policy range, a cancellation.
 Note that once we go off policy we should clear any grace records. Going off
 policy, by definition, means that policy coverage has been revoked from
 which it
 follows that a revoked policy can not be in grace.
\end{cpar}%
\end{lcom}%
\@x{ reduce ( m ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} m . startDt \.{\geq} policy . startDt}%
\@x{\@s{16.4} \.{\land} m . endDt \.{=} policy . endDt}%
\@x{\@s{16.4} \.{\land} m . startDt \.{<} m . endDt}%
 \@x{\@s{16.4} \.{\land} policy \.{'} \.{=} [ policy {\EXCEPT} {\bang} . endDt
 \.{=} m . startDt ]}%
 \@x{\@s{16.4} \.{\land} \.{\LET} outstanding \.{\defeq} \{ i\@s{1.65} \.{\in}
 invsIssued \.{:} i . settlementStatus \.{=}\@w{Outstanding} \}}%
 \@x{\@s{47.91} invalidates\@s{4.15} \.{\defeq} \{ o \.{\in} outstanding \.{:}
 o . startDt \.{\geq} m . startDt \}}%
 \@x{\@s{27.51} \.{\IN} \.{\land} invsIssued \.{'} \.{=} ( invsIssued
 \.{\,\backslash\,} invalidates ) \.{\cup}}%
 \@x{\@s{108.13} \{ [ i {\EXCEPT} {\bang} . settlementStatus \.{=}\@w{Settled}
 ,\,}%
 \@x{\@s{162.01} {\bang} . settlementType \.{=}\@w{WrittenOff} ] \.{:} i
 \.{\in} invalidates \}}%
\@x{\@s{47.91} \.{\land} time \.{'} \.{=} time \.{+} 1}%
\@x{\@s{47.91} \.{\land} {\IF} outstanding \.{=} invalidates}%
\@x{\@s{56.11} \.{\THEN} gracesUnsettled \.{'} \.{=} \{ \}}%
\@x{\@s{56.11} \.{\ELSE} {\UNCHANGED} {\langle} gracesUnsettled {\rangle}}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 Change is a generic operations the updates policy coverage, an endorsement.
}%
\@xx{}%
\@x{ change ( m ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
 \@x{\@s{16.4} \.{\land} policy . startDt \.{\leq} m . startDt \.{\land} m .
 startDt \.{<} policy . endDt}%
\@x{\@s{16.4} \.{\land} m . endDt \.{=} policy . endDt}%
\@x{\@s{16.4} \.{\land} m . startDt \.{<} m . endDt}%
\@x{\@s{16.4} \.{\land} invsIssued \.{'} \.{=} invsIssued \.{\cup} \{ [}%
\@x{\@s{48.01} totalDue \.{\mapsto} 10 ,\,}%
\@x{\@s{48.01} startDt \.{\mapsto} m . startDt ,\,}%
 \@x{\@s{48.01} dueDt \.{\mapsto} max ( m . startDt \.{+} 1 ,\, time \.{+} 1 )
 ,\,}%
\@x{\@s{48.01} settlementStatus \.{\mapsto}\@w{Outstanding} ,\,}%
\@x{\@s{48.01} settlementType \.{\mapsto}\@w{Null}}%
\@x{\@s{31.61} ] \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} policy ,\, gracesUnsettled
 {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 We have discussed grace processing above. For emphasis here, note that the
 guard clause
 below only adds a grace record if there are no unsettled records associated
 with the
 policy.
\end{cpar}%
\end{lcom}%
\@x{ doAutoGrace ( inv ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} gracesUnsettled \.{=} \{ \}}%
 \@x{\@s{16.4} \.{\land} inv . settlementStatus \.{=}\@w{Outstanding}
 \.{\land} inv . dueDt \.{=} time}%
 \@x{\@s{16.4} \.{\land} gracesUnsettled \.{'} \.{=} gracesUnsettled \.{\cup}
 \{ [}%
\@x{\@s{48.01} startDt \.{\mapsto} time ,\,}%
\@x{\@s{48.01} endDt \.{\mapsto} time \.{+} 2}%
\@x{\@s{31.61} ] \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} policy ,\, invsIssued
 {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Auto lapse will cancel the whole policy and that requires settling all the
 invoices,
 not just 1 particular invoice, associated with the grace record. In the
 implementation
 that invoice cancellation details are handled in the
 \ensuremath{CancellationsService
}%
\end{cpar}%
\end{lcom}%
\@x{ doAutoLapse ( g ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} g . endDt \.{=} time}%
 \@x{\@s{16.4} \.{\land} policy \.{'}\@s{6.93} \.{=} [ policy {\EXCEPT}
 {\bang} . endDt \.{=} policy . startDt ]}%
 \@x{\@s{16.4} \.{\land} \.{\LET} outstanding \.{\defeq} \{ i \.{\in}
 invsIssued \.{:} i . settlementStatus \.{=}\@w{Outstanding} \}}%
 \@x{\@s{47.91} settled \.{\defeq} \{ i \.{\in} invsIssued \.{:} i .
 settlementStatus \.{=}\@w{Settled} \}}%
\@x{\@s{27.51} \.{\IN} invsIssued \.{'} \.{=} settled \.{\cup}}%
 \@x{\@s{72.51} \{ [ i {\EXCEPT} {\bang} . settlementStatus \.{=}\@w{Settled}
 ,\,}%
 \@x{\@s{126.39} {\bang} . settlementType \.{=}\@w{WrittenOff} ] \.{:} i
 \.{\in} outstanding \}}%
\@x{\@s{16.4} \.{\land} gracesUnsettled \.{'} \.{=} \{ \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 When payments come in, the framework checks to see if the policy is in grace.
 If it is
 and the current payment will settle all outstandiing invoices, then the
 payment routines
 can also settle the grace record, bringing the policy out of grace. This
 processing
 rule tends to be hard to understand for engineers, so remember paying one
 invoice
 generally does not get a policy out of grace, all outstanding invoices have
 to be
 paid.
\end{cpar}%
\end{lcom}%
\@x{ doPayment ( inv ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} inv . settlementStatus \.{=}\@w{Outstanding}}%
 \@x{\@s{16.4} \.{\land} invsIssued \.{'} \.{=} ( invsIssued
 \.{\,\backslash\,} \{ inv \} ) \.{\cup} \{}%
 \@x{\@s{48.01} [ inv {\EXCEPT} {\bang} . settlementStatus \.{=}\@w{Settled}
 ,\, {\bang} . settlementType \.{=}\@w{Paid} ]}%
\@x{\@s{48.01} \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
 \@x{\@s{16.4} \.{\land} \.{\LET} overdueInvs \.{\defeq} overdueInvoices (
 invsIssued \.{\,\backslash\,} \{ inv \} )}%
 \@x{\@s{27.51} \.{\IN} {\CASE} overdueInvs \.{=} \{ \} \.{\land}
 gracesUnsettled \.{=} \{ \} \.{\rightarrow}}%
\@x{\@s{77.98} {\UNCHANGED} {\langle} policy ,\, gracesUnsettled {\rangle}}%
 \@x{\@s{56.11} {\Box}\@s{10.30} overdueInvs \.{=} \{ \} \.{\land}
 gracesUnsettled \.{\neq} \{ \} \.{\rightarrow}}%
\@x{\@s{77.98} \.{\land} gracesUnsettled \.{'} \.{=} \{ \}}%
\@x{\@s{77.98} \.{\land} {\UNCHANGED} policy}%
\@x{\@s{56.11} {\Box}\@s{10.30} overdueInvs \.{\neq} \{ \} \.{\rightarrow}}%
\@x{\@s{77.98} {\UNCHANGED} {\langle} policy ,\, gracesUnsettled {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 When we reverse payment we want to (1) reset the due date, and grace date of
 the
 affected invoice. This prevents reversals of older invoices from immediately
 causing
 the policy to go into grace and immediately after be cancelled. This is a
 side effect
 that customers will find hard to understand. Presumably if a customer has to
 pay some
 time must be given to them to do so before cancelling their policy. (2) We
 dont want to
 reverse payments on policies that are fully cancelled. To reinterate a
 similiar
 thought above, it does not make sense in that a customer would have to
 suddenly owe
 money on a previous invoice and yet the coverage that invoice is based on is
 not being
 offered to them. Customer but also the code will expect this convention so
 if it is
 violated the automated lapse code will refuse to cooperate and someone,
 maybe you,
 will get a late night call.
\end{cpar}%
\end{lcom}%
\@x{ doRevPayment ( inv ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} policy . startDt \.{<} policy . endDt}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} inv . settlementStatus \.{=}\@w{Settled}}%
 \@x{\@s{16.4} \.{\land} invsIssued \.{'} \.{=} ( invsIssued
 \.{\,\backslash\,} \{ inv \} ) \.{\cup} \{}%
 \@x{\@s{48.01} [ inv {\EXCEPT} {\bang} . settlementStatus
 \.{=}\@w{Outstanding} ,\,}%
\@x{\@s{107.17} {\bang} . settlementType \.{=}\@w{Null} ,\,}%
\@x{\@s{107.17} {\bang} . dueDt \.{=} max ( inv . dueDt ,\, time \.{+} 1 ) ]}%
\@x{\@s{48.01} \}}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} policy ,\, gracesUnsettled
 {\rangle}}%
\@pvspace{16.0pt}%
\@x{ tick \.{\defeq}}%
\@x{\@s{16.4} \.{\land} {\lnot} autoJobCanRun ( time )}%
\@x{\@s{16.4} \.{\land} time \.{<} endTime}%
\@x{\@s{16.4} \.{\land} time \.{'} \.{=} time \.{+} 1}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} invsIssued ,\, policy ,\,
 gracesUnsettled {\rangle}}%
\@pvspace{8.0pt}%
\@x{ term \.{\defeq}}%
\@x{\@s{16.4} \.{\land} time \.{=} endTime}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} invsIssued ,\, policy ,\,
 gracesUnsettled ,\, time {\rangle}}%
\@pvspace{8.0pt}%
\@x{ Init \.{\defeq}}%
\@x{\@s{16.4} \.{\land} \exists\, p \.{\in} Policy \.{:}}%
\@x{\@s{48.01} \.{\land} p . startDt \.{<} p . endDt}%
\@x{\@s{48.01} \.{\land} policy \.{=} p}%
\@x{\@s{16.4} \.{\land} time \.{=} 0}%
\@x{\@s{16.4} \.{\land} invsIssued \.{=} \{ [}%
\@x{\@s{48.01} totalDue \.{\mapsto} 10 ,\,}%
\@x{\@s{48.01} startDt \.{\mapsto} policy . startDt ,\,}%
\@x{\@s{48.01} dueDt \.{\mapsto} policy . startDt \.{+} 1 ,\,}%
\@x{\@s{48.01} settlementStatus \.{\mapsto}\@w{Outstanding} ,\,}%
\@x{\@s{48.01} settlementType \.{\mapsto}\@w{Null}}%
\@x{\@s{31.61} ] \}}%
\@x{\@s{16.4} \.{\land} gracesUnsettled \.{=} \{ \}}%
\@pvspace{8.0pt}%
\@x{ Next \.{\defeq}}%
\@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Modification \.{:}}%
\@x{\@s{48.01} \.{\lor} change ( m )}%
\@x{\@s{48.01} \.{\lor} extend ( m )}%
\@x{\@s{48.01} \.{\lor} reduce ( m )}%
\@x{\@s{16.4} \.{\lor} \exists\, inv \.{\in} invsIssued \.{:}}%
\@x{\@s{48.01} \.{\lor} doAutoGrace ( inv )}%
\@x{\@s{48.01} \.{\lor} doPayment ( inv )}%
\@x{\@s{48.01} \.{\lor} doRevPayment ( inv )}%
 \@x{\@s{16.4} \.{\lor} \exists\, g \.{\in} gracesUnsettled \.{:} doAutoLapse
 ( g )}%
\@x{\@s{16.4} \.{\lor} term}%
\@pvspace{8.0pt}%
 \@x{ Spec \.{\defeq} Init \.{\land} {\Box} [ Next ]_{ {\langle} invsIssued
 ,\, policy ,\, gracesUnsettled ,\, time {\rangle}}}%
\@x{}\bottombar\@xx{}%
\setboolean{shading}{false}
\begin{lcom}{0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
\ensuremath{\.{\,\backslash\,}}* \ensuremath{Modification} History
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Wed}
 \ensuremath{Dec} 23 15:54:04 \ensuremath{PST} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Created \ensuremath{Wed} \ensuremath{Nov} 18
 17:58:19 \ensuremath{PST} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\end{lcom}%
