\tlatex
\setboolean{shading}{true}
\@x{}\moduleLeftDash\@xx{ {\MODULE} CancellationCtx1}\moduleRightDash\@xx{}%
\@x{ {\EXTENDS} Integers ,\, Policy}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 In this specification I only model cancellations and renewals processes, but
 I can not
 ignore the effects of other concurrent endorsement or renewals that may
 happen during
 those processes. I model possible endorsements and renewals with the constant
 \ensuremath{EndorsementOrRenewal} which represents such a modification, in
 the accepted state.
\end{cpar}%
\end{lcom}%
\@x{ {\CONSTANTS} EndorsementOrRenewal}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
The no config values indicates that a there is no cancellation configuration
 on the system and at that legacy cancellation logic should be called.
\end{cpar}%
\end{lcom}%
\@x{ NoConfig \.{\defeq} {\CHOOSE} x \.{:} x \.{\notin} {\BOOLEAN}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
A reinstatement is type of modification. A reinstatement starts at some time
 and reactivates a policy upto one of its previous end timestamps. A
 reinstatement has
 two specialized attributes one, specified in configuration, is the
 \ensuremath{auto\_reinstate}: boolean
 variable. If this variable is true for a reinstatement a payment recieved on
 a finalized
 reinstatement should cause the reinstatement to be issued. The second
 attribute is a
 \ensuremath{deadline\_ts} which is the last time at which the reinstatement
 can be issued.
\end{cpar}%
\end{lcom}%
\@x{ Reinstatements \.{\defeq} [}%
\@x{\@s{16.4} type \.{:} \{\@w{Reinstatement} \} ,\,}%
\@x{\@s{16.4} state \.{:} ModificationState ,\,}%
\@x{\@s{16.4} start\_timestamp \.{:} TimeRange ,\,}%
\@x{\@s{16.4} end\_timestamp \.{:} TimeRange ,\,}%
\@x{\@s{16.4} auto\_reinstate \.{:} {\BOOLEAN} ,\,}%
\@x{\@s{16.4} deadline\_ts \.{:} TimeRange ,\,}%
\@x{\@s{16.4} product\_revision \.{:} 0 \.{\dotdot} maxRevision}%
\@x{ ]}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Its possible that different behaviors can be defined for different
 cancelation reasons,
 using liquid scripting. Inside \ensuremath{Java} \ensuremath{API} code, the
 cancellation reason, Lapsed, is used
 to mark cancellations that happen through the action of the automated
 Grace-Lapse routines.
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{CancellationReasons \.{\defeq} \{\mbox{``}Lapse\mbox{''},\,
 \@w{OtherReason}\}
}%
\end{cpar}%
\end{lcom}%
\@x{ CancellationReasons \.{\defeq} \{\@w{OtherReason} \}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
A cancellation is also a special type of modification. Though not modeled
 in this specification cancellations should record their cancellation reason.
\end{cpar}%
\end{lcom}%
\@x{ Cancellations \.{\defeq} [}%
\@x{\@s{16.4} type \.{:} \{\@w{Cancellation} \} ,\,}%
\@x{\@s{16.4} state \.{:} ModificationState ,\,}%
\@x{\@s{16.4} start\_timestamp \.{:} TimeRange ,\,}%
\@x{\@s{16.4} end\_timestamp \.{:} TimeRange ,\,}%
\@x{\@s{16.4} product\_revision \.{:} 0 \.{\dotdot} maxRevision}%
\@x{ ]}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
Cancellations and reinstatements, like endorsements and renewals, are recorded
 as they are created in the history of policy modifications. Some of these
 modifications
 will take effect, by being issued, others will never be issued. In all
 cases, though,
 modifications retain an identity to which documents and invoices can be
 attached.
 The characteristic of the modifications, which gives them a group
 commonality, is
 that they can operate to change liability of the parties to the contract
\end{cpar}%
\end{lcom}%
\@x{}\bottombar\@xx{}%
\setboolean{shading}{false}
\begin{lcom}{0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
\ensuremath{\.{\,\backslash\,}}* Modification History
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Tue}
 \ensuremath{Sep} 15 17:29:27 \ensuremath{PDT} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Thu}
 \ensuremath{Jul} 16 16:33:53 \ensuremath{PDT} 2020 by \ensuremath{marco
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Created Sat \ensuremath{Jun} 27 21:12:19
 \ensuremath{PDT} 2020 by \ensuremath{ASUS
}%
\end{cpar}%
\end{lcom}%
