\tlatex
\setboolean{shading}{true}
\@x{}\moduleLeftDash\@xx{ {\MODULE} FeesFlatMch1}\moduleRightDash\@xx{}%
 \@x{ {\EXTENDS} FeesFlatCtx1 ,\, IntervalOps ,\, TLC ,\, Sequences ,\,
 FiniteSets}%
\@pvspace{8.0pt}%
\@x{ {\CONSTANTS} maxSteps}%
\@x{ {\VARIABLES} policy ,\, chs ,\, fees ,\, cancelQ ,\, pc}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 In this specification we consider the behavior of a single flat fee as it is
 acted on
 by cancellations and reinstatements. The flat fee is modeled by list where
 the first
 element records the fee state as it was initially created. Policy
 modifications change
 this initial state by appending records to the list. The last element then
 records
 the latest state of the fee.
 As the width of the flat fee changes we would like the amount to stay
 constant. The
 only exception to this expectation is when the width is equal to zero. In
 the zero
 width case modifications have move the fee outside the policy range and
 setting it to
 zero removes all charges associated with it.
\end{cpar}%
\end{lcom}%
\@x{}\midbar\@xx{}%
\@x{ oneOf ( set ) \.{\defeq} {\CHOOSE} x \.{\in} set \.{:} {\TRUE}}%
\@pvspace{8.0pt}%
 \@x{ leastOf ( pchs ) \.{\defeq} {\CHOOSE} x \.{\in} pchs \.{:} ( \A\, ch
 \.{\in} pchs \.{:} x . start\_ts \.{\leq} ch . start\_ts )}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Do an interval subtraction. If the result is the empty set then return a zero
 width
 fee.
\end{cpar}%
\end{lcom}%
 \@x{ safeSubtract ( fee ,\, mod ) \.{\defeq} \.{\LET} tmpSet \.{\defeq}
 subtract ( fee ,\, mod )}%
\@x{\@s{16.4} \.{\IN} {\IF} tmpSet \.{=} \{ \}}%
 \@x{\@s{36.79} \.{\THEN} [ fee {\EXCEPT} {\bang} . amount \.{=} 0 ,\, {\bang}
 . end\_ts \.{=} fee . start\_ts ]}%
\@x{\@s{36.79} \.{\ELSE} oneOf ( tmpSet )}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 Try to expand a fee extent stoping when we either hit the \ensuremath{max}
 extent of the fee or a
 gap in the policy coverage.
\end{cpar}%
\end{lcom}%
\@x{ extendOnReinstate ( latest ,\, first ,\, mod ) \.{\defeq}}%
\@x{\@s{16.4} {\IF} latest . start\_ts \.{=} latest . end\_ts}%
\@x{\@s{16.4} \.{\THEN} \.{\LET} is \.{\defeq} intersect ( first ,\, mod )}%
\@x{\@s{47.71} \.{\IN} {\IF} is \.{=} \{ \}}%
\@x{\@s{68.11} \.{\THEN} latest}%
\@x{\@s{68.11} \.{\ELSE} oneOf ( is )}%
\@x{\@s{16.4} \.{\ELSE} {\IF} latest . start\_ts \.{<} latest . end\_ts}%
 \@x{\@s{47.71} \.{\THEN} {\CASE} latest . end\_ts \.{<} mod . start\_ts
 \.{\rightarrow} latest}%
\@x{\@s{79.02} {\Box} latest . end\_ts \.{=} mod . start\_ts \.{\rightarrow}}%
 \@x{\@s{87.22} \.{\LET} is2\@s{4.26} \.{\defeq} intersect ( first ,\, [
 start\_ts \.{\mapsto} latest . start\_ts ,\,}%
\@x{\@s{212.60} end\_ts \.{\mapsto} mod . end\_ts ] )}%
 \@x{\@s{107.62} tmp \.{\defeq} Assert ( Cardinality ( is2 ) \.{=} 1
 ,\,\@w{cardinality\ should\ be\ 1} )}%
\@x{\@s{87.22} \.{\IN} oneOf ( is2 )}%
 \@x{\@s{79.02} {\Box} {\OTHER} \.{\rightarrow} Assert ( {\FALSE} ,\,\@w{bad\
 case} )}%
\@x{\@s{47.71} \.{\ELSE} Assert ( {\FALSE} ,\,\@w{bad\ if} )}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 The policy characteristics set has one or more non overlapping coverage
 intervals,
 and characteristic is contained within the policy bounds. For the special
 case where
 the width of the policy is zero, there should be one zero width
 characteristic.
\end{cpar}%
\end{lcom}%
\@x{ invPolicy \.{\defeq}}%
\@x{\@s{16.4} \.{\land} policy \.{\in} Interval}%
\@x{\@s{16.4} \.{\land} policy . start\_ts \.{\leq} policy . end\_ts}%
 \@x{\@s{16.4} \.{\land} policy . start\_ts \.{=} policy . end\_ts
 \.{\implies} Cardinality ( chs ) \.{=} 1}%
 \@x{\@s{16.4} \.{\land} \A\, ch \.{\in} chs \.{:} ch . start\_ts \.{\leq} ch
 . end\_ts}%
 \@x{\@s{16.4} \.{\land} \A\, ch1 ,\, ch2 \.{\in} chs \.{:} \.{\lor} ch1 \.{=}
 ch2}%
\@x{\@s{108.08} \.{\lor} notOverlaps ( ch1 ,\, ch2 )}%
\@x{\@s{16.4} \.{\land} \A\, ch \.{\in} chs \.{:} contains ( policy ,\, ch )}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 If there are no unreinstated cancellations then the policy must have a
 non-zero width.
}%
\@xx{}%
 \@x{ invQ \.{\defeq} ( cancelQ \.{=} \{ \} \.{\land} pc \.{\neq} 0 )
 \.{\implies} policy . start\_ts \.{<} policy . end\_ts}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 A flat fee must always be contained within the bounds of the initial fee
 version. If
 the policy is fully cancelled then the amount of the fee must be zero,
 though a zero
 amount fee does not imply that the policy is fully cancelled.
\end{cpar}%
\end{lcom}%
\@x{ invFees \.{\defeq}}%
\@x{\@s{16.4} \.{\land} \.{\LET} latest \.{\defeq} fees [ Len ( fees ) ]}%
 \@x{\@s{27.51} \.{\IN} \.{\land} width ( latest ) \.{=} 0 \.{\equiv} latest .
 amount \.{=} 0}%
 \@x{\@s{47.91} \.{\land} width ( latest ) \.{\neq} 0 \.{\equiv} latest .
 amount \.{=} 4}%
 \@x{\@s{47.91} \.{\land} latest . start\_ts \.{\geq} Head ( fees ) .
 start\_ts}%
\@x{\@s{47.91} \.{\land} latest . end\_ts \.{\leq} Head ( fees ) . end\_ts}%
\@x{\@s{47.91} \.{\land} width ( latest )\@s{0.07} \.{\neq} 0 \.{\implies} (}%
\@x{\@s{71.32} \.{\lor} latest . end\_ts \.{\leq} policy . end\_ts}%
\@x{\@s{71.32} \.{\lor} latest . start\_ts \.{\geq} policy . start\_ts )}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
When a policy is fully cancelled then all of its flat fees must also be fully
 cancelled. If a policy has an extent and any of its policy characteristics
 overlap
 the initial state of the fee, then the latest state of the fee must have an
 extent
 and its amount must be equal to the amount of the initial state. Lastly, if
 latest
 state of a fee is zero then it must be the case that it does not overlap any
 of the
 policy characteristics.
\end{cpar}%
\end{lcom}%
\@x{ invPolicyFees \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} latest \.{\defeq} fees [ Len ( fees ) ]}%
 \@x{\@s{16.4} \.{\IN} \.{\land} policy . start\_ts \.{=} policy . end\_ts
 \.{\implies} latest . amount \.{=} 0}%
 \@x{\@s{36.79} \.{\land} ( width ( policy ) \.{>} 0\@s{4.1} \.{\land}
 \exists\, ch \.{\in} chs \.{:} overlaps ( ch ,\, Head ( fees ) ) )}%
\@x{\@s{75.82} \.{\implies} latest . amount \.{=} 4}%
 \@x{\@s{36.79} \.{\land} latest . amount \.{=} 0 \.{\implies} {\lnot} (
 \exists\, ch \.{\in} chs \.{:} overlaps ( ch ,\, latest ) )}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 A new version of a fee should always differ in some way from the version that
 it
 replaces.
\end{cpar}%
\end{lcom}%
\@x{ invRepeatFree \.{\defeq}}%
\@x{\@s{16.4} \.{\LET} len \.{\defeq} Len ( fees )}%
 \@x{\@s{16.4} \.{\IN} len \.{\geq} 2 \.{\implies} {\lnot} ( \.{\land} fees [
 len\@s{0.21} \.{-} 1 ] . start\_ts \.{=} fees [ len ] . start\_ts}%
 \@x{\@s{95.00} \.{\land} fees [ len \.{-} 1 ] . end\_ts \.{=} fees [ len ] .
 end\_ts )}%
\@x{}\midbar\@xx{}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 On reinstatment we would like to restore any reduced flat fees back to their
 initial
 width. This in not always possible though for a variety of reason. The
 reinstatement
 may not expand the policy range to encompass the initial extent of the fee
 or there
 could be gaps in the policy coverage. Because of this, in determining the
 extent of
 a fee after a reinstatment we take the coverage period of the policy as an
 ordered
 list of intervals separated by gaps and examine their ordered intersections
 with the
 initial fee. At a high level, after any reinstatement the restored fee
 extent should
 equal the first of the above ordered intersections.
 The high level intent is realized below with an iterative calculation, that,
 to a first
 approximation, trys to expand the current fee\mbox{'}s extent as long as the
 reinstatement
 starts at the lastest fee version\mbox{'}s end timestamp.
\end{cpar}%
\end{lcom}%
\@x{ reinstateOp ( m ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} pc \.{<} maxSteps}%
\@x{\@s{16.4} \.{\land} m . type \.{\in} \{\@w{Reinstate} \}}%
\@x{\@s{16.4} \.{\land} cancelQ \.{\neq} \{ \}}%
\@x{\@s{16.4} \.{\land} \.{\LET} prevMod \.{\defeq} leastOf ( cancelQ )}%
 \@x{\@s{27.51} \.{\IN} prevMod . start\_ts \.{\leq} m . start\_ts \.{\land}
 prevMod . end\_ts \.{=} m . end\_ts \.{\land} m . start\_ts \.{<} m .
 end\_ts}%
 \@x{\@s{16.4} \.{\land} \.{\LET} nextStartTs \.{\defeq} {\IF} policy .
 start\_ts \.{=} policy . end\_ts}%
\@x{\@s{118.64} \.{\THEN} m . start\_ts}%
\@x{\@s{118.64} \.{\ELSE} policy . start\_ts}%
 \@x{\@s{47.91} nextPolicy \.{\defeq} [ policy {\EXCEPT} {\bang} . start\_ts
 \.{=} nextStartTs ,\, {\bang} . end\_ts \.{=} m . end\_ts ]}%
 \@x{\@s{47.91} nextChs \.{\defeq} {\IF} policy . start\_ts \.{=} policy .
 end\_ts}%
 \@x{\@s{102.15} \.{\THEN} \{ [ start\_ts \.{\mapsto} m . start\_ts ,\,
 end\_ts \.{\mapsto} m . end\_ts ] \}}%
\@x{\@s{102.15} \.{\ELSE} {\UNION} \{}%
\@x{\@s{137.56} chs ,\,}%
 \@x{\@s{137.56} \{ [ start\_ts \.{\mapsto} m . start\_ts ,\, end\_ts
 \.{\mapsto} m . end\_ts ] \}}%
\@x{\@s{110.35} \}}%
\@x{\@s{47.91} latestV\@s{3.09} \.{\defeq} fees [ Len ( fees ) ]}%
\@x{\@s{47.91} firstV \.{\defeq} fees [ 1 ]}%
 \@x{\@s{47.91} nextD \.{\defeq} extendOnReinstate ( latestV ,\, firstV ,\, m
 )}%
\@x{\@s{27.51} \.{\IN} \.{\land} policy \.{'} \.{=} nextPolicy}%
\@x{\@s{47.91} \.{\land} chs \.{'} \.{=} nextChs}%
 \@x{\@s{47.91} \.{\land} cancelQ \.{'} \.{=} cancelQ \.{\,\backslash\,} \{
 leastOf ( cancelQ ) \}}%
\@x{\@s{47.91} \.{\land} pc \.{'} \.{=} pc \.{+} 1}%
 \@x{\@s{47.91} \.{\land} {\IF} nextD . start\_ts \.{\neq} latestV . start\_ts
 \.{\lor} nextD . end\_ts \.{\neq} latestV . end\_ts}%
 \@x{\@s{59.02} \.{\THEN} fees \.{'} \.{=} Append ( fees ,\, [ firstV
 {\EXCEPT} {\bang} . pc \.{=} pc ,\,}%
\@x{\@s{254.63} {\bang} . start\_ts \.{=} nextD . start\_ts ,\,}%
\@x{\@s{254.63} {\bang} . end\_ts \.{=} nextD . end\_ts ] )}%
\@x{\@s{59.02} \.{\ELSE} {\UNCHANGED} {\langle} fees {\rangle}}%
\@pvspace{8.0pt}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 On cancellation if a flat fee is shrunk to zero width then its amount shrinks
 to zero.
 Otherwise the amount will be a constant value and the range of the fee will
 be in the
 policy range.
\end{cpar}%
\end{lcom}%
\@x{ cancelOp ( m ) \.{\defeq}}%
\@x{\@s{16.4} \.{\land} pc \.{<} maxSteps}%
\@x{\@s{16.4} \.{\land} m . type \.{\in} \{\@w{Cancel} \}}%
\@x{\@s{16.4} \.{\land} m . start\_ts \.{<} m . end\_ts}%
\@x{\@s{16.4} \.{\land} m . start\_ts \.{\geq} policy . start\_ts}%
\@x{\@s{16.4} \.{\land} m . end\_ts \.{=} policy . end\_ts}%
\@x{\@s{16.4} \.{\land} \.{\LET} latestV \.{\defeq} fees [ Len ( fees ) ]}%
 \@x{\@s{47.91} nextV \.{\defeq} [ safeSubtract ( latestV ,\, m ) {\EXCEPT}
 {\bang} . pc \.{=} pc ]}%
 \@x{\@s{47.91} nextPolicy \.{\defeq} [ policy {\EXCEPT} {\bang} . end\_ts
 \.{=} m . start\_ts ]}%
\@x{\@s{47.91} nextChs \.{\defeq} subtractAll ( chs ,\, m )}%
\@x{\@s{27.51} \.{\IN} \.{\land} policy \.{'} \.{=} nextPolicy}%
\@x{\@s{47.91} \.{\land} chs \.{'} \.{=} {\IF} nextChs \.{=} \{ \}}%
 \@x{\@s{89.78} \.{\THEN} \{ [ start\_ts \.{\mapsto} policy . start\_ts ,\,
 end\_ts \.{\mapsto} policy . start\_ts ] \}}%
\@x{\@s{89.78} \.{\ELSE} nextChs}%
\@x{\@s{47.91} \.{\land} cancelQ \.{'} \.{=} cancelQ \.{\cup} \{ m \}}%
\@x{\@s{47.91} \.{\land} pc \.{'} \.{=} pc \.{+} 1}%
 \@x{\@s{47.91} \.{\land} {\IF} nextV . start\_ts \.{\neq} latestV . start\_ts
 \.{\lor} nextV . end\_ts \.{\neq} latestV . end\_ts}%
\@x{\@s{59.02} \.{\THEN} fees \.{'} \.{=} Append ( fees ,\, nextV )}%
\@x{\@s{59.02} \.{\ELSE} {\UNCHANGED} {\langle} fees {\rangle}}%
\@pvspace{8.0pt}%
\@x{ done \.{\defeq}}%
\@x{\@s{16.4} \.{\land} pc \.{=} maxSteps}%
 \@x{\@s{16.4} \.{\land} {\UNCHANGED} {\langle} policy ,\, chs ,\, fees ,\,
 cancelQ ,\, pc {\rangle}}%
\@pvspace{8.0pt}%
\@x{}\midbar\@xx{}%
\begin{lcom}{7.5}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 We start of with a generalized policy and its single policy characteristic
 and a
 single fee which may reside anywhere inside the policy interval. Without
 loss of
 generality, we can deduce the behavior of all fees from this starting point.
\end{cpar}%
\end{lcom}%
 \@x{ Init\@s{4.12} \.{\defeq} \exists\, t1 ,\, t2 \.{\in} 0 \.{\dotdot}
 maxTime \.{:}}%
\@x{\@s{56.23} \.{\land} t1 \.{<} t2}%
 \@x{\@s{56.23} \.{\land} policy \.{=} [ start\_ts \.{\mapsto} 0 ,\, end\_ts
 \.{\mapsto} maxTime ]}%
 \@x{\@s{56.23} \.{\land} chs \.{=} \{ [ start\_ts \.{\mapsto} 0 ,\, end\_ts
 \.{\mapsto} maxTime ] \}}%
 \@x{\@s{56.23} \.{\land} fees \.{=} {\langle} [ pc \.{\mapsto} 0 ,\, amount
 \.{\mapsto} 4 ,\, start\_ts \.{\mapsto} t1 ,\, end\_ts \.{\mapsto} t2 ]
 {\rangle}}%
\@x{\@s{56.23} \.{\land} cancelQ \.{=} \{ \}}%
\@x{\@s{56.23} \.{\land} pc \.{=} 1}%
\@pvspace{8.0pt}%
\@x{ Next \.{\defeq}}%
 \@x{\@s{16.4} \.{\lor} \exists\, m \.{\in} Modification \.{:} \.{\lor}
 cancelOp ( m )}%
\@x{\@s{119.80} \.{\lor} reinstateOp ( m )}%
\@x{\@s{16.4} \.{\lor} done}%
\@pvspace{8.0pt}%
 \@x{ Spec \.{\defeq} Init \.{\land} {\Box} [ Next ]_{ {\langle} policy ,\,
 chs ,\, fees ,\, cancelQ ,\, pc {\rangle}}}%
\@pvspace{8.0pt}%
\@x{}\bottombar\@xx{}%
\setboolean{shading}{false}
\begin{lcom}{0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
\ensuremath{\.{\,\backslash\,}}* \ensuremath{Modification} History
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Thu}
 \ensuremath{Jul} 15 16:11:29 \ensuremath{PDT} 2021 by \ensuremath{ASUS
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Created \ensuremath{Wed} \ensuremath{Jul} 14
 19:53:26 \ensuremath{PDT} 2021 by \ensuremath{ASUS
}%
\end{cpar}%
\end{lcom}%
