\tlatex
\setboolean{shading}{true}
\@x{}\moduleLeftDash\@xx{ {\MODULE} DocConsolidateCtx0}\moduleRightDash\@xx{}%
\@x{ {\EXTENDS} Integers}%
\@pvspace{8.0pt}%
\@x{}%
\@y{\@s{0}%
 The minimal status codes necessary to track the progress of async jobs.
}%
\@xx{}%
 \@x{ ProcessStatus \.{\defeq} \{\@w{InProcess} ,\,\@w{Error} ,\,\@w{Success}
 \}}%
\@pvspace{8.0pt}%
\begin{lcom}{2.5}%
\begin{cpar}{0}{T}{F}{5.0}{0}{}%
 We specify each document as being either a single document or a composite
 document
\end{cpar}%
\begin{cpar}{1}{F}{F}{0}{0}{}%
made up of multiple single documents.
\end{cpar}%
\end{lcom}%
\@x{ CollationType \.{\defeq} \{\@w{Single} ,\,\@w{Multiple} \}}%
\@pvspace{8.0pt}%
\begin{lcom}{2.5}%
\begin{cpar}{0}{T}{F}{5.0}{0}{}%
 There are two processes. One that generates a document in some format and a
 second
\end{cpar}%
\begin{cpar}{1}{F}{F}{0}{0}{}%
 type of process that takes existing pdf documents and consolidates them into
 a single
 pdf document.
\end{cpar}%
\end{lcom}%
\@x{ Process \.{\defeq} \{\@w{DocGen} ,\,\@w{DocConsolidate} \}}%
\@pvspace{8.0pt}%
\begin{lcom}{2.5}%
\begin{cpar}{0}{T}{F}{5.0}{0}{}%
 A document request can create either a single document or a consolidated
 document in
\end{cpar}%
\begin{cpar}{1}{F}{F}{0}{0}{}%
 large object storage. A single document create request will have an empty
 \ensuremath{componentDocs
 } set. A consolidated document request will supply a list of existing
 document locators
 that reference single documents.
\end{cpar}%
\end{lcom}%
\@x{ DocRequest \.{\defeq} [}%
\@x{\@s{16.4} id \.{:} Int ,\,}%
\@x{\@s{16.4} process \.{:} Process ,\,}%
\@x{\@s{16.4} componentDocs \.{:} {\SUBSET} Int ,\,}%
\@x{\@s{16.4} processCount \.{:} Int}%
\@x{ ]}%
\@pvspace{8.0pt}%
\begin{lcom}{2.5}%
\begin{cpar}{0}{T}{F}{5.0}{0}{}%
 Record, below, represents a document record that has been added to the
 \ensuremath{policy\_document
}%
\end{cpar}%
\begin{cpar}{1}{F}{F}{0}{0}{}%
 table in the database. The record, here, includes just the fields needed by
 this
 document processing specification.
\end{cpar}%
\end{lcom}%
\@x{ Record \.{\defeq} [}%
\@x{\@s{16.4} id \.{:} Int ,\,}%
\@x{\@s{16.4} collationType \.{:} CollationType ,\,}%
\@x{\@s{16.4} processStatus\@s{0.31} \.{:} ProcessStatus}%
\@x{ ]}%
\@pvspace{8.0pt}%
\@x{}\bottombar\@xx{}%
\setboolean{shading}{false}
\begin{lcom}{0}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
\ensuremath{\.{\,\backslash\,}}* Modification History
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Tue}
 \ensuremath{Oct} 12 09:21:02 \ensuremath{PDT} 2021 by \ensuremath{marco
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* Last modified \ensuremath{Wed}
 \ensuremath{Oct} 06 12:57:41 \ensuremath{PDT} 2021 by \ensuremath{ASUS
}%
\end{cpar}%
\begin{cpar}{0}{F}{F}{0}{0}{}%
 \ensuremath{\.{\,\backslash\,}}* \ensuremath{Created} \ensuremath{Fri}
 \ensuremath{Sep} 17 18:39:27 \ensuremath{PDT} 2021 by \ensuremath{ASUS
}%
\end{cpar}%
\end{lcom}%
