\motto{I call it "The Question."
Obviously it should be applied
as much to one's own thinking as to
others'. It consists of asking in your
own mind, on hearing any scientific
explanation or theory put forward, "But
sir, what experiment could disprove
your hypothesis?"}
\chapter{Scheduled Jobs}
\label{intro:jobs} % Always give a unique label

\abstract{}

\section{Grace and Lapse}
\label{sec:jobs:1}
In addition to cancellations that can happen through the API, it's also possible for policies to be canceled automatically by
the system. This automated cancellation happens when a policy has outstanding invoices which have not been paid. The system
scheduled grace job flags outstanding invoices and the scheduled lapse job, after some time, will eventually cancel the policies
associated with those flagged invoices. Below is a simplified model of the process, which details the essential points of
understanding for the jobs.
\import{chJobs/}{AutoGraceLapseInvoiceCtx0-sa.tex}
\import{chJobs/}{AutoGraceLapseInvoiceMch0-sa.tex}

\section{Document Consolidation}
\label{sec:jobs:2}
During a modification's transition into the Accepted state, documents associated with that modification are generated.
The documents are generated from templates written in Liquid code and the templates output either a text or HTML formatted
string. If desired the system
can take this string output and convert it into a PDF document. The final form of the document is then stored in Amazon S3.

In addition to generating documents some customers would like to consolidate a subset of the existing documents as well, and this has
let to the development of the document consolidation plugin and associated consolidation routines. The main consideration in
developing the consolidation routines has been to avoid generating the consolidated documents synchronously with the accept transition.
Document generation has historically been a large part of the accept transition's service time so there is some trepidation around adding
more to what already exists. There is also reason to believe that some customers may have consolidation tasks that are one or two orders of
magnitude larger than the usual size of the document generation tasks that currently run semi-synchronously. These two considerations have
let to an asynchronous consolidate implementation which is discussed below.
\import{chJobs/}{DocConsolidateCtx0-sa.tex}
\import{chJobs/}{DocConsolidateMch0-sa.tex}
